### 2020-08-04 confirm-activity/tex/intro.tex
more reorganizing
merge discussion and future work, and rename

\paragraph{\bf Motivation.} Although rewards computation and activity monitoring are reasonable for the first iteration of the network, we acknowledge that it suffers from two main problems:
\begin{itemize}
\setlength{\itemsep}{0pt}
\item The revenue computation (both fees and subsidy) is agnostic to the number of requests Ursula serves. Thus, an active Ursula who may serve a huge number of re-encryption requests, and one who does not receive any requests (or more importantly, a malicious/lazy Ursula that does not answer Bob's requests), will both collect the same amount of revenue if they hold identical policies.

\item Confirming being online is flawed in the sense that the function call that Ursula makes does not require any input or proofs on providing the service, or even being online and responsive. Ursula can stay offline the majority of the time and not respond to Bobs' requests, then come online merely to call this function. This allows Ursula to collect both subsidy and fees without doing all (or even most) of the necessary work. Even worse, Ursula will be able to get her stake back once it unlocks.
\end{itemize}

@@

\paragraph{\bf Organization.}
We begin with outlining the adopted threat and network model, in Section~\ref{threat-network-model}, followed by an overview of some of the cryptographic primitives that we use in Section~\ref{prelim}. Then, we present the proposed solutions for confirm availability in Section~\ref{confirm-availability} and those for confirming service activity in Section~\ref{confirm-service-activity}. After that, we briefly discuss the trade-offs and requirements of each of these solutions along with some usage recommendations in Section~\ref{discussion}. Lastly, in Section~\ref{future-work} we conclude with highlighting some of our future work directions.

>>>>

\paragraph{\bf Motivation.} Although rewards computation and activity monitoring are reasonable for the first iteration of the network, we acknowledge that it suffers from two main problems:
\begin{itemize}
\setlength{\itemsep}{0pt}
\item Confirming being online is flawed in the sense that the function call that Ursula makes does not require any input or proofs on providing the service, or even being online and responsive. Ursula can stay offline the majority of the time and not respond to Bobs' requests, then come online merely to call this function. This allows Ursula to collect both subsidy and fees without doing all (or even most) of the necessary work. Even worse, Ursula will be able to get her stake back once it unlocks.

\item The revenue computation (both fees and subsidy) is agnostic to the number of requests Ursula serves. Thus, an active Ursula who may serve a huge number of re-encryption requests, and one who does not receive any requests (or more importantly, a malicious/lazy Ursula that does not answer Bob's requests), will both collect the same amount of revenue if they hold identical policies.
\end{itemize}

@@

\paragraph{\bf Organization.}
We begin with outlining the adopted threat and network model, in Section~\ref{threat-network-model}, followed by an overview of some of the cryptographic primitives that we use in Section~\ref{prelim}. Then, we present the proposed solutions for confirm availability in Section~\ref{confirm-availability} and those for confirming service activity in Section~\ref{confirm-service-activity}. Lastly, we briefly discuss the trade-offs and requirements of each of these solutions along with some usage recommendations and future work directions in Section~\ref{discussion}.
